Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX Format\titlenote{(Produces the permission block, and copyright information). For use with SIG-ALTERNATE.CLS. Supported by ACM.}

### 2015-02-06 paperGecco.tex
paperGecco.tex con el formato terminado ahora el texto

\documentclass{sig-alternate}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx, epsfig}

\usepackage{url}
\urldef{\mailsa}\path|{mgarenas,nrico,deromero,pacv,jmerelo}@ugr.es|

\begin{document}
\conferenceinfo{GECCO'15,} {July 11-15, 2015, Madrid, Spain.}
    \CopyrightYear{2015}
    \crdata{TBA}
    \clubpenalty=10000
    \widowpenalty = 10000
%\mainmatter  % start of an individual contribution
%

\title{Using evolutionary algorithms to optimize the estimation of a diffusion process}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{6} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Nuria Rico\titlenote{Dr.~Nuria Rico Castro.}\\
       \affaddr{Faculty of Science University of Granada}\\
       \email{nrico@ugr.es}
% 2nd. author
\alignauthor
M.G. Arenas\titlenote{Dr. ~ M. Isabel García Arenas.}\\
       \affaddr{ETSIIT - University of Granada}\\
       \email{mgarenas@ugr.es}
% 3rd. author
\alignauthor
D. Romero\titlenote{Dr. ~Desirée Romero.}\\
       \affaddr{ETSIIT - University of Granada}\\
       \email{deromero@ugr.es}
\alignauthor
P. A. Castillo\titlenote{Dr. ~Pedro A. Castillo Valdivieso.}\\
       \affaddr{ETSIIT - University of Granada}\\
       \email{pacv@ugr.es}
\alignauthor
J. M. Crespo\titlenote{Dr. ~J. M. Crespo.}\\
       \affaddr{ETSIIT - University of Granada}\\
       \email{crespo@ugr.es}
%\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor J. J. Merelo\\
       \affaddr{Dr. Juan Julián Merelo Guervós}\\
       \affaddr{ETSIIT-University of Granada}\\
       \email{jjmerelo@ugr.es}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
%\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\begin{figure*}[htb]
  \centering
\begin{tabular}{ c c }
  \epsfig{file=graf1prueba.eps,width=.50\textwidth} & \epsfig{file=graf2prueba.eps,width=.50\textwidth} \\
  $\sigma^2=10^{-5}$ & $\sigma^2=10^{-4}$ \\
  \epsfig{file=graf3prueba.eps,width=.50\textwidth} & \epsfig{file=graf4prueba.eps,width=.50\textwidth} \\
  $\sigma^2=10^{-3}$ & $\sigma^2=10^{-2}$\\
\end{tabular}
\caption{Simulated paths for Gompertz-lognormal processes from $t_0=1$ to $t_{500}=100$, with values $m=1$, $\beta=0.2$, and $c=0.013$ and different values of noise; $\sigma^2=10^{-5}$, $\sigma^2=10^{-4}$, $\sigma^2=10^{-3}$ and  $\sigma^2=10^{-2}$. Black lines highlight the paths last value $x_{i;500}$ are maximum, minimum and the quartiles of the output range. } \label{1:figura:path}
\end{figure*}

@@

\bibitem{proceedingBol}
Guti{\'e}rrez, R., Rico, N., Rom{\'a}n, P., Romero, D., Torres, F.:
Un nuevo proceso de difusi{\'o}n para modelizar patrones de crecimiento mixto exponencial-Gompertz. XXX Congreso Nacional SEIO. Libro de Actas, pp. 1--15 (2007)

@@

\end{thebibliography}

>>>>

% This is "sig-alternate.tex" V2.0 May 2012
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate}

\begin{document}
\conferenceinfo{GECCO'15,} {July 11-15, 2015, Madrid, Spain.}
    \CopyrightYear{2015}
    \crdata{TBA}
    \clubpenalty=10000
    \widowpenalty = 10000
%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{6} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
%Nuria Rico\titlenote{Dr.~Nuria Rico Castro.}\\
%       \affaddr{Faculty of Science }\\
%       \affaddr{University of Granada}\\
%       \email{nrico@ugr.es}       
Nuria Rico\titlenote{Dr.~Rico}\\
       \affaddr{Statistics and Operational Research}\\
       \affaddr{University of Granada}\\
       \affaddr{Granada, Spain}\\
       \email{nrico@ugr.es}
% 2nd. author
\alignauthor
M. G. Arenas\titlenote{Dr. ~Arenas}\\
       \affaddr{Computer Architecture}\\
       \affaddr{University of Granada}\\
       \affaddr{Granada, Spain}\\
       \email{mgarenas@ugr.es}
% 3rd. author
\alignauthor 
Desir\'{e}e Romero\titlenote{Dr. ~Romero}\\
       \affaddr{Statistics and Operational Research}\\
       \affaddr{University of Granada}\\
       \affaddr{Granada, Spain}\\
       \email{deromero@ugr.es}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor 
P. A. Castillo\titlenote{Dr. ~Castillo}\\
       \affaddr{Computer Architecture}\\
       \affaddr{University of Granada}\\
       \affaddr{Granada, Spain}\\
       \email{pacv@ugr.es}
% 5th. author
\alignauthor
J. M. Crespo\titlenote{Dr. ~Crespo}\\
       \affaddr{Statistics and Operational Research}\\
       \affaddr{University of Granada}\\
       \affaddr{Granada, Spain}\\
       \email{crespo@ugr.es}
% 6th. author
\alignauthor
J. J. Merelo\titlenote{Dr. ~Merelo}\\
       \affaddr{Computer Arquitecture}\\
       \affaddr{University of Granada}\\
       \affaddr{Granada, Spain}\\
       \email{jmerelo@ugr.es}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{1 Feb 2015}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

\begin{figure*}[htb]
  \centering
\begin{tabular}{ c c }
  \epsfig{file=graf1prueba.eps,width=.40\textwidth} & \epsfig{file=graf2prueba.eps,width=.40\textwidth} \\
  $\sigma^2=10^{-5}$ & $\sigma^2=10^{-4}$ \\
  \epsfig{file=graf3prueba.eps,width=.40\textwidth} & \epsfig{file=graf4prueba.eps,width=.40\textwidth} \\
  $\sigma^2=10^{-3}$ & $\sigma^2=10^{-2}$\\
\end{tabular}
\caption{Simulated paths for Gompertz-lognormal processes from $t_0=1$ to $t_{500}=100$, with values $m=1$, $\beta=0.2$, and $c=0.013$ and different values of noise; $\sigma^2=10^{-5}$, $\sigma^2=10^{-4}$, $\sigma^2=10^{-3}$ and  $\sigma^2=10^{-2}$. Black lines highlight the paths last value $x_{i;500}$ are maximum, minimum and the quartiles of the output range. } \label{1:figura:path}
\end{figure*}

@@

%\bibitem{proceedingBol}
%Guti{\'e}rrez, R., Rico, N., Rom{\'a}n, P., Romero, D., Torres, F.:
%Un nuevo proceso de difusi{\'o}n para modelizar patrones de crecimiento mixto exponencial-Gompertz. XXX Congreso Nacional SEIO. Libro de Actas, pp. 1--15 (2007)

@@

\end{thebibliography}
%\bibliography{comparingbib}  % sigproc.bib is the name of the Bibliography in this case
